Reproducibility in Plant Pathology

### 2020-07-24 README.rmd
Fix my contact information
Update Dockerfile directions in README

@@

+61 (7) 4831 1948   <adam.sparks@usq.edu.au>

>>>>

#### The Docker Instance

Get the latest instance from Dockerhub, launch it and go to `localhost:8787` in your browser.
Login with `rstudio`, password is `rstudio`.

```
docker pull adamhsparks/reproducibility_in_plant_pathology
docker run -d -p 8787:8787
```

#### The Paper

A script, `knit_paper.R` is located in `analysis/paper/knit_paper.R` that will knit the Word document

@@

+61 (7) 4631 1948   <adam.sparks@usq.edu.au>
